Language learning via recursive pragmatic reasoning

### 2013-05-31 praglearn.tex
more text

\title{Learning to communicate using recursive pragmatic
  reasoning about other agents}
% \title{Learning words via recursive pragmatic reasoning about other agents}
% : The blessing of social anxiety - not a huge fan of colon titles

@@

\newcommand{\word}{\text{word}}
\newcommand{\obj}{\text{object}}
\newcommand{\lex}{\text{lexicon}}
%\newcommand{\prior}{P_{\text{prior}}(\obj | \text{context})}
\newcommand{\prior}{P_{\text{prior}}(\obj)}

@@

Natural language is a powerful tool for conveying meaning in
context. Consider
``it's raining,'' ``I ate some of the cookies,'' or ``can you close
the window?'' In each, a listener must go beyond the literal meaning
of the words to fill in contextual details (``it's raining here and
now''), infer that a stronger alternative is not true (``I ate some
but not all of the cookies''), or more generally infer the speaker's
communicative goal (``I want you to close the window right now because
I'm cold''), a process known as \textit{pragmatic reasoning}. 
This kind of pragmatic reasoning is core to language use,

Following this intuition, theories of pragmatic communication frame
the process of language comprehension as inference about the
generating goal of an utterance given a rational speaker
\cite{grice1975,dale1995,frank2012}. For example, a listener might
reason, ``if she had wanted me to think `all' of the cookies, she
would have said `all'---but she didn't. Hence `all' must not be true
and she must have eaten some {\it but not all} of the cookies.'' This
kind of counterfactual reasoning has a recursive character to it:
listener models speaker (who may in turn be modeling a listener).

Even before they are proficient language users, children learn the
meanings of words from their pattern of use in context. For example,
in demonstrations of the ``disambiguation effect,'' a novel word
(e.g.~``dax'') is used in a context containing both a novel and a
familiar object. From quite young, children tend to make the inference
that ``dax'' refers to the novel object \cite{markman1988}. In another
demonstration, even young toddlers can extract mappings between words
and objects from a pattern of individually-ambiguous co-occurrences
between pairs of words and pairs of objects \cite{smith2008}. Taking
inspiration from children's learning prowess, recent work in the field
of grounded language learning has explored the possibility that even
relatively complex word meanings can be inferred from corpus data
(e.g.~\cite{zettlemoyer2005,chen2008,frank2009,kwiatkowski2010,johnson2012}).

Recursive pragmatic inferences such as those described above could be
an important part of language learning.\footnote{Very young children
  make inferences that are often labeled as ``pragmatic'' in that they
  involve reasoning about context \cite{clark1988,baldwin1993}, though
  they also show weaknesses in specific inferences (e.g.~strengthening
  ``some'' to ``some but not all'' \cite{papafragou2003}). Here we
  remain agnostic about the age at which children are able to make
  such inferences robustly, as it may vary depending on the linguistic
  materials being used in the inference \cite{barner2011}.} For
example, the disambiguation inference described above can emerge from
such reasoning (``why would the speaker have said ``dax'' if there was
a word for the known object that she knew I would know'')
\cite{clark1988}. In addition, there are a variety of intriguing cases
in which listeners seem to create situation- and task-specific ways of
referring to particular objects. For example, when asked to refer to
idiosyncratic geometric shapes, over the course of an experimental
session, participants create conventionalized descriptions that allow
them to perform accurately even though they do not begin with a shared
label \cite{krauss1964,clark1986}. Yet models of grounded language
learning have failed to take pragmatic factors into account.

@@

@@

\subsection{Paradoxes in optimal models of pragmatic learning}
% When modelling human behavior, it's useful to begin with optimal
% models; this has the advantage that when we are then forced to
% deviate from the purely rational approach, it's generally in a
% theoretically interpretable way. However,
Multi-agent interactions are difficult to model in a normative or
optimal framework without falling prey to paradox. For example,
consider a simple model of the agents in the above game. First we
define a \textit{literal listener} $L_0$. This agent has a
\textit{lexicon} of associations between words and meanings;
specifically, it assigns each word $w$ a vector of numbers in $(0, 1)$ describing the extent
to which this word provides evidence for each possible object\footnote{We
  assume words refer directly to objects, rather than to abstract
  semantic features. Our simplification is without loss of
  generalization, however, because we can interpret our model as
  marginalizing over such a representation, with our literal
  $P_\lex(\obj | \word) = \sum_\text{features} P(\obj |
  \text{features}) P_\lex(\text{features} | \word)$.}.%
If we assume the listener simply re-weights their prior expectation   
about what is referred to using their lexicon:
\begin{align*}
P_{L_0}(\obj | \word, \lex) &\propto \lex(\word, \obj) \times \prior.
\end{align*}
Because of the normalization in this equation, there is a systematic but unimportant symmetry among lexicons; we 
remove this by assuming the lexicon sums to $1$ over objects for each word.
Confronted with such a listener, a probabilistically rational speaker
should attempt to choose a word which soft-maximizes the probability
that the listener will assign to the target object---modulated by the
effort or cost associated with producing this word:
\begin{align*}
P_{S_1}(\word | \obj, \lex) &\propto \exp\Big(\lambda \big(\log P_{L_0}(\obj | \word, \lex) - \text{cost}(\word)\big)\Big).
\end{align*}
But given this speaker, then the naive $L_0$ strategy is not
optimal. Instead, listeners should use Bayes rule to invert the
speaker's decision procedure \cite{frank2012}:
\begin{align*}
P_{L_2}(\obj | \word, \lex) &\propto P_{S_1}(\word | \obj, \lex) \times \prior.
\end{align*}
Now the paradox becomes apparent. Given such a listener, it is no
longer optimal for speakers to implement strategy $S_1$; instead, they
should implement strategy $S_3$ which soft-maximizes $P_{L_2}$ instead
of $P_{L_0}$. And then listeners ought to implement $L_4$, and so on.

One option is to continue iterating such
strategies until reaching a fixed point equilibrium. While this
strategy guarantees that each agent will behave normatively given the
other agent's strategy, there is no guarantee that such strategies
will be near the system's global optimum. More importantly, is there much
evidence that humans do not use such equilibrium strategies; their behavior in language
games (and in other games \cite{camerer2004}) can be well-modeled as
implementing $S_n$ or $L_n$ for some small $n$
\cite{frank2012}. Following this work, we recurse a finite (small)
number of times. The consequence is that one agent, implementing
$S_n$, is fully optimal with respect to the game, while the other,
implementing $L_{n-1}$, is only nearly optimal---off by a single
recursion.

@@

One final problem is that there is nothing
constraining speaker and listener to use the same language under this
model. In principle, so long as the listener has a good model of the
speaker, and the speaker has a good model of the listener, then
communication succeeds. This result clearly presents a dramatic
mismatch to typical human communication, which almost never proceeds
with distinct languages spoken by each participant.

@@

Assumption (a) corresponds to the lexicographer's illusion: Naive
language users will argue vociferously that words have specific
meanings, even though these meanings are unobservable to everyone who
purportedly uses them. It also explains why learners speak the
language they hear (rather than some private language that they assume
listeners will eventually learn): Under assumption (a), observing
other speakers' behavior provides data about not just that speaker's
idiosyncratic lexicon, but the consensus lexicon. Assumption (b)
avoids the explosion of hyper$^n$-distributions described above: If
agent $n$ knows the lexicon, they assume that all lower agents do as
well, reducing to the original tractable model without
uncertainty. And assumption (c) introduces a limited form of
uncertainty at the top level, and thus the potential for learning.
% Everything else follows by applying standard Bayesian reasoning
% given these assumptions.

Formally, let an unadorned $L$ and $S$ denote our convention-based
listener and speaker. By assumption (c), the top-level listener has uncertainty over the lexicon; if the lexicon were known they would draw inferences as in $L_n$ above:
%\begin{align*}
%  P_L(\obj | \word) &= P_{S_{n-1}}(\word | \obj, \text{$L$'s data}) \times \prior \\
%    &= \sum_\lex P_{S_{n-1}}(\word | \obj, \lex) \times P(\lex | \text{$L$'s data}) \times \prior. \\
%    &= P_{L_n}(\obj | \word, \text{$L$'s data}). \\
%  P_S(\word | \obj) &\propto \exp\Big(\lambda \big(\log P_{L_n}(\obj | \word, \text{$S$'s data}) - \text{cost}(\word)\big)\Big).
%\end{align*}
%
\begin{align*}
  P_L(\obj | \word, \text{$L$'s data}) &=  \sum_\lex P_{L_n}(\obj | \word, \lex) P(\lex | \text{$L$'s data}) \\
\end{align*}
Here $L$'s data consists of $S$'s utterances together with whatever
other information $L$ may have about their meaning (e.g.~from
contextual clues). 
By assumption (b), $L$ treats these  utterances
as samples from the knowledgeable speaker $S_{n-1}$, not $S$, and thus
as being informative about the lexicon. For instance, when the data is a set of fully observed 
word-referent pairs $\{w_i, o_i\}$:
\begin{align*}
  P(\lex | \text{$L$'s data}) \propto P(\lex) \prod_i P_{S_{n-1}}(w_i|o_i,  \lex)
\end{align*}
The top-level speaker attempts to select the word which soft-maximizes their utility, with utility now being defined in terms of the informativity of the expectation (over lexicons) that the listener will have for at the right referent\footnote{An alternative model would have the speaker take the expectation over informativity, instead of the informativity of the expectation.}:
\begin{align*}
  P_S(\word | \obj, \text{$S$'s data}) &\propto \exp\Big(\lambda \big(\log  \sum_\lex P_{L_{n-1}}(\obj | \word, \lex) P(\lex|\text{$S$'s data}) - \text{cost}(\word)\big)\Big)
\end{align*}
Here $P(\lex|\text{$S$'s data}$ is defined similarly, when $S$ observes
$L$'s interpretations of various utterances, and treats them as
samples from $L_n$, not $L$.

%In several important cases, these assumptions are as close to rational
%as possible within the finite-recursion framework. If $L_n(\obj |
%\word, \text{$S$'s data})$ and $L_n(\obj | \word, \text{$L$'s data})$
%coincide, then $S$ is fully normative and $L$ is off by only a single
%recursion. This case in particular includes all previous experiments
%using this pragmatic reasoning framework, which considered only
%single-turn interactions where $\text{$L$'s data} = \text{$S$'s data}
%= \emptyset$.

If the speaker has enough data that their
uncertainty is effectively non-existent, then it becomes normative for
their partner to treat them as being fully knowledgeable, and this is
a reasonable description of the child language learning case. In
general, though, in arbitrary multi-turn interactions in which both
agents have non-trivial uncertainty, this model induces complex and
non-normative learning dynamics.

@@

Many sets of words in natural language form scales in which each term
refers to successively stronger restrictions on the situations
compatible with the term. ``Some'' and ``all'' form a scale of this
type. While ``I ate some of the cookies'' is compatible with the
followup ``in fact, I ate {\it all} of the cookies,'' the reverse is
not true. ``Might'' and ``must'' are another example, as are ``OK,''
``good,'' and ``excellent.'' All of these scales allow for {\it scalar
  implicatures} \cite{grice1975}: if a speaker uses a weaker term, a
listener is licensed to infer that the stronger term was not true in
this situation. So although ``I ate some of the cookies'' could in
principle be compatible with eating all of them, the listener is lead
to believe that ``some but not all'' is the likely state of
affairs. We use the term {\it specificity implicature} here (following
\cite{bergen2012}) to denote that we are agnostic about whether such
implicatures are conventionalized or whether they use a
contextually-defined scale.

The recursive pragmatic reasoning portions of our model capture
findings on specificity implicature. Consider a representation of
scalar implicature as a matrix $\left[
    \begin{array}{cc}
      0.5 & 0.5 \\
      0 & 1
    \end{array}
  \right]$, where rows show the words ``some'' and ``all'' and columns
  indicate worlds where {\sc some but not all} and {\sc all} are true,
  respectively, capturing the regularity that ``some'' can be said of
  situations where {\sc all} is actually the case. Assuming uniform
  costs for the two words, a rational speaker confronted with such a
  lexicon will prefer to say ``some'' only when they mean \textsc{some
    but not all}, and this is therefore the interpretation that a
  rational listener will place on ``some'' as well. To simulate this
  situation, we place a Dirichlet(10, 10) prior on the meaning of
  \textit{some} and a Dirichlet(1, 10) prior on the meaning of
  \textit{all}, giving speaker probabilities of
  $\left[
    \begin{array}{cc}
      1.00 & 0.00 \\
      0.00 & 1.00
    \end{array}
  \right]$
and listener probabilities of
$\left[
    \begin{array}{cc}
      .86 & .14 \\
      .03 & .97
    \end{array}
  \right]$. These revised interpretation probabilities minimize
  ambiguity (with weight concentrated on the diagonal), capturing the specificity implicature.

>>>>

\title{Language learning via recursive pragmatic reasoning}
% \title{Learning words via recursive pragmatic reasoning about other agents}
% : The blessing of social anxiety - not a huge fan of colon titles

@@

\newcommand{\word}{\text{word}}
\newcommand{\obj}{\text{object}}
\newcommand{\lex}{\text{lexicon}}
\newcommand{\prior}{P_{\text{prior}}(\obj | \text{context})}

@@

Natural language is a powerful tool for conveying meaning in
context. Consider the utterances
``it's raining,'' ``I ate some of the cookies,'' or ``can you close
the window?'' In each, a listener must go beyond the literal meaning
of the words to fill in contextual details (``it's raining here and
now''), infer that a stronger alternative is not true (``I ate some
but not all of the cookies''), or more generally infer the speaker's
communicative goal (``I want you to close the window right now because
I'm cold''), a process known as \textit{pragmatic reasoning}. Theories of pragmatics frame
the process of language comprehension as inference about the
generating goal of an utterance given a rational speaker
\cite{grice1975,dale1995,frank2012}. For example, a listener might
reason, ``if she had wanted me to think `all' of the cookies, she
would have said `all'---but she didn't. Hence `all' must not be true
and she must have eaten some {\it but not all} of the cookies.'' This kind of reasoning is core to language use.

But pragmatic reasoning often intersects with language learning as
well. In both adults and children, uncertainty about word meanings is
common, and often considering speakers' pragmatic goals can help to resolve this uncertainty. For example,
if a novel word is used in a context containing both a novel and a
familiar object, young children can make the inference
that the novel word refers to the novel object \cite{markman1988}.\footnote{Very young children
  make inferences that are often labeled as ``pragmatic'' in that they
  involve reasoning about context \cite{clark1988,baldwin1993}, though
  they also show weaknesses in specific inferences (e.g.~strengthening
  {\sc some} to {\sc some but not all} \cite{papafragou2003}). Here we
  remain agnostic about the age at which children are able to make
  such inferences robustly, as it may vary depending on the linguistic
  materials being used in the inference \cite{barner2011}.} For adults
who are proficient language users, there are also a variety of intriguing cases
in which listeners seem to create situation- and task-specific ways of
referring to particular objects. For example, when asked to refer to
idiosyncratic geometric shapes, over the course of an experimental
session, participants create conventionalized descriptions that allow
them to perform accurately even though they do not begin with a shared
label \cite{krauss1964,clark1986}. In both of these examples, reasoning about another person's goals informs language learners' estimates of what words are likely to mean.

% Recursive pragmatic inferences such as those described above could be
% an important part of language learning. For
% example, the disambiguation inference described above can emerge from
% such reasoning (``why would the speaker have said ``dax'' if there was
% a word for the known object that she knew I would know'')
% \cite{clark1988}.Yet models of grounded language
% learning have failed to take pragmatic factors into account.

Despite this intersection, there is relatively little work that takes pragmatic reasoning into account when considering language learning in context. Recent work on grounded language learning has attempted to learn large sets of (sometimes relatively complex) word meanings directly from corpus data
(e.g.~\cite{zettlemoyer2005,chen2008,frank2009,kwiatkowski2010,johnson2012}). And
a number of models have begun to formalize the consequences of
pragmatic reasoning in situations where limited learning takes place
\cite{golland2010,frank2012,bergen2012}. But as yet these two strands
of research have not been brought together so that the implications of
pragmatics for learning can be investigated directly.

% \footnote{Very young children
%   make inferences that are often labeled as ``pragmatic'' in that they
%   involve reasoning about context \cite{clark1988,baldwin1993}, though
%   they also show weaknesses in specific inferences (e.g.~strengthening
%   {\sc some} to {\sc some but not all} \cite{papafragou2003}). Here we
%   remain agnostic about the age at which children are able to make
%   such inferences robustly, as it may vary depending on the linguistic
%   materials being used in the inference \cite{barner2011}.}

@@

% This
% kind of counterfactual reasoning has a recursive character to it:
% listener models speaker (who may in turn be modeling a listener).

% Even before they are proficient language users, children learn the
% meanings of words from their pattern of use in context.

% In another
% demonstration, even young toddlers can extract mappings between words
% and objects from a pattern of individually-ambiguous co-occurrences
% between pairs of words and pairs of objects \cite{smith2008}.

%

@@

\subsection{Paradoxes in optimal models of pragmatic learning}
% When modelling human behavior, it's useful to begin with optimal
% models; this has the advantage that when we are then forced to
% deviate from the purely rational approach, it's generally in a
% theoretically interpretable way. However,
Multi-agent interactions are difficult to model in a normative or
optimal framework without falling prey to paradox. For example,
consider a simple model of the agents in the above game. First we
define a \textit{literal listener} $L_0$. This agent has a
\textit{lexicon} which probabilistically maps words to meanings;
specifically, it assigns each word $w$ a vector describing the extent
to which this word provides evidence for each possible object.\footnote{We
  assume words refer directly to objects, rather than to abstract
  semantic features. Our simplification is without loss of
  generalization, however, because we can interpret our model as
  marginalizing over such a representation, with our literal
  $P_\lex(\obj | \word) = \sum_\text{features} P(\obj |
  \text{features}) P_\lex(\text{features} | \word)$.} Each entry in
the vector is in $(0, 1)$, and together they sum to 1:
\begin{align*}
P_{L_0}(\obj | \word, \lex) &\propto \lex(\word, \obj) \times \prior.
\end{align*}
Confronted with such a listener, a probabilistically rational speaker
should attempt to choose a word which soft-maximizes the probability
that the listener will assign to the target object---modulated by the
effort or cost associated with producing this word:
\begin{align*}
P_{S_1}(\word | \obj, \lex) &\propto \exp\Big(\lambda \big(\log P_{L_0}(\obj | \word, \lex) - \text{cost}(\word)\big)\Big).
\end{align*}
But given this speaker, then the naive $L_0$ strategy is not
optimal. Instead, listeners should use Bayes rule to invert the
speaker's decision procedure \cite{frank2012}:
\begin{align*}
P_{L_2}(\obj | \word, \lex) &\propto P_{S_1}(\word | \obj, \lex) \times \prior.
\end{align*}
Now the paradox becomes apparent. Given such a listener, it is no
longer optimal for speakers to implement strategy $S_1$; instead, they
should implement strategy $S_3$ which soft-maximizes $P_{L_2}$ instead
of $P_{L_0}$. And then listeners ought to implement $L_4$, and so on.

One computationally expensive option is to continue iterating such
strategies until reaching a fixed point equilibrium. While this
strategy guarantees that each agent will behave normatively given the
other agent's strategy, there is no guarantee that such strategies
will be near the system's global optimum; equilibrium strategies make
up only a small subspace of all possible strategies. Nor is there much
evidence the humans find such equilibria; their behavior in language
games (and in other games \cite{camerer2004}) can be well-modeled as
implementing $S_n$ or $L_n$ for some small $n$
\cite{frank2012}. Following this work, we recurse a finite (small)
number of times. The consequence is that one agent, implementing
$S_n$, is fully optimal with respect to the game, while the other,
implementing $L_{n-1}$, is nearly optimal---off by only a single
recursion.

@@

To add insult to injury, one final problem is that there is nothing
constraining speaker and listener to use the same language under this
model. In principle, so long as the listener has a good model of the
speaker, and the speaker has a good model of the listener, then
communication succeeds. This result clearly presents a dramatic
mismatch to typical human communication, which almost never proceeds
with distinct languages spoken by each participant.

@@

Assumption (a) corresponds to the lexicographer's illusion: Naive
language users will argue vociferously that words have specific
meanings, even though these meanings are unobservable to everyone who
purportedly uses them. It also explains why learners speak the
language they hear (rather than some private language that they assume
listeners will eventually learn): Under assumption (a), observing
other speakers' behavior provides data about not just that speaker's
idiosyncratic lexicon, but the consensus lexicon. Assumption (b)
avoids the explosion of hyper$^n$-distributions described above: If
agent $n$ knows the lexicon, they assume that all lower agents do as
well, reducing to the original tractable model without
uncertainty. And assumption (c) introduces a limited form of
uncertainty, and thus the potential for learning.
% Everything else follows by applying standard Bayesian reasoning
% given these assumptions.

Formally, let an unadorned $L$ and $S$ denote our socially-anxious
listener and speaker. $L$ inverts their marginal distribution over the
speaker; $S$ soft-maximizes their marginal distribution over the
listener. With $L_i$ and $S_i$ as above, this gives:
\begin{align*}
  P_L(\obj | \word) &= P_{S_{n-1}}(\word | \obj, \text{$L$'s data}) \times \prior \\
    &= \sum_\lex P_{S_{n-1}}(\word | \obj, \lex) \times P(\lex | \text{$L$'s data}) \times \prior \\
    &= P_{L_n}(\obj | \word, \text{$L$'s data}). \\
  P_S(\word | \obj) &\propto \exp\Big(\lambda \big(\log P_{L_n}(\obj | \word, \text{$S$'s data}) - \text{cost}(\word)\big)\Big).
\end{align*}
Here $L$'s data consists of $S$'s utterances together with whatever
other information $L$ may have about their meaning (e.g.~from
contextual clues). By assumption (b), $L$ treats these as utterances
as samples from the knowledgeable speaker $S_{n-1}$, not $S$, and thus
as being informative about the lexicon. Similarly, $S$ may observe
$L$'s interpretations of various utterances, and will treat these as
samples from $L_n$, not $L$.

In several important cases, these assumptions are as close to rational
as possible within the finite-recursion framework. If $L_n(\obj |
\word, \text{$S$'s data})$ and $L_n(\obj | \word, \text{$L$'s data})$
coincide, then $S$ is fully normative and $L$ is off by only a single
recursion. This case in particular includes all previous experiments
using this pragmatic reasoning framework, which considered only
single-turn interactions where $\text{$L$'s data} = \text{$S$'s data}
= \emptyset$. Alternatively, if one agent has enough data that their
uncertainty is effectively non-existent, then it becomes normative for
their partner to treat them as being fully knowledgeable, and this is
a reasonable description of the child language learning case. In
general, though, in arbitrary multi-turn interactions in which both
agents have non-trivial uncertainty, this model induces complex and
non-normative learning dynamics.

@@

Many sets of words in natural language form scales in which each term
refers to successively stronger restrictions on the situations
compatible with the term. ``Some'' and ``all'' form a scale of this
type. While ``I ate some of the cookies'' is compatible with the
followup ``in fact, I ate {\it all} of the cookies,'' the reverse is
not true. ``Might'' and ``must'' are another example, as are ``OK,''
``good,'' and ``excellent.'' All of these scales allow for {\it scalar
  implicatures} \cite{grice1975}: if a speaker uses a weaker term, a
listener is licensed to infer that the stronger term was not true in
this situation. So although ``I ate some of the cookies'' could in
principle be compatible with eating {\sc all} of them, the listener is lead
to believe that {\sc some-but-not-all}' is the likely state of
affairs. We use the term {\it specificity implicature} here (following
\cite{bergen2012}) to denote that we are agnostic about whether such
implicatures are conventionalized or whether they use a
contextually-defined scale.

The recursive pragmatic reasoning portions of our model capture
findings on specificity implicature. Consider a representation of
scalar implicature as a matrix $\left[
    \begin{array}{cc}
      0.5 & 0.5 \\
      0 & 1
    \end{array}
  \right]$, where rows show the words ``some'' and ``all'' and columns
  indicate worlds where {\sc some but not all} and {\sc all} are true,
  respectively, capturing the regularity that ``some'' can be said of
  situations where {\sc all} is actually the case. Assuming uniform
  costs for the two words, a rational speaker confronted with such a
  lexicon will prefer to say ``some'' only when they mean \textsc{some
    but not all}, and this is therefore the interpretation that a
  rational listener will place on ``some'' as well. To simulate this
  situation, we place a Dirichlet(10, 10) prior on the meaning of
``some'' and a Dirichlet(1, 10) prior on the meaning of
``some'', giving speaker probabilities of
  $\left[
    \begin{array}{cc}
      1.00 & 0.00 \\
      0.00 & 1.00
    \end{array}
  \right]$
and listener probabilities of
$\left[
    \begin{array}{cc}
      .86 & .14 \\
      .03 & .97
    \end{array}
  \right]$. These revised interpretation probabilities minimize
  ambiguity (with weight concentrated on the diagonal), capturing the specificity implicature.
